### 2017-06-10 README.Rmd
Added Two Means example

Infer: a grammar for statistical inference
---

The objective of this package is to perform statistical inference using a grammar that illustrates the underlying concepts and a format that coheres with the `tidyverse`.

@@

@@

>>>>

Infer: a grammar for statistical inference

---

The objective of this package is to perform statistical inference using a grammar that illustrates the underlying concepts and a format that coheres with the `tidyverse`. To participate in the discussion surrounding the development of this package, please see the issues.

@@

#### Examples

These examples assume that `mtcars` has been overwritten so that the variables
`cyl`, `vs`, `am`, `gear`, and `carb` are `factor`s:

```
mtcars <- as.data.frame(mtcars) %>%
  mutate(cyl = factor(cyl),
         vs = factor(vs),
         am = factor(am),
         gear = factor(gear),
         carb = factor(carb))
```

One categorical (2 level) variable
```
mtcars %>%
  select(am) %>%
  hypothesis(null = "p = 25") %>% # would require string parsing
  generate(reps = 100, type = "permute") %>% # here it’d be doing simulation
  calculate(stat = "prop") #
```

Two categorical (2 level) variables
```
mtcars %>%
  select(am, vs) %>%
  hypothesis(null = "independence") %>% # 
  generate(reps = 100, type = "permute") %>%
  calculate(stat = "diff in prop") #
```

One categorical (>2 level) - GoF
```
mtcars %>%
  select(cyl) %>%
  hypothesis(null = "p1 = .33, p2 = .33, p3 = .33") %>%
  generate(reps = 100, type = "permute") %>%
  calculate(stat = "chisq")
```

Two categorical (>2 level) variables
```
mtcars %>%
  select(cyl, am) %>%
  hypothesis(null = "independence") %>%
  generate(reps = 100, type = "permute") %>%
  calculate(stat = "chisq")
```

One numerical variable one categorical (2 levels) (diff in means)
```
mtcars %>%
  select(mpg, am) %>%
  hypothesis(null = "equal means") %>%
  generate(reps = 100, type = "permute") %>%
  calculate(stat = "diff in means")
```

One numerical one categorical (>2 levels) -  ANOVA
```
mtcars %>%
  select(mpg, cyl) %>%
  hypothesis(null = "equal means") %>%
  generate(reps = 100, type = "permute") %>%
  calculate(stat = "F")
```

Two numerical vars - SLR
```
mtcars %>%
  select(mpg, hp) %>%
  hypothesis(null = "independence") %>% # or "slope = 0"
  generate(reps = 100, type = "permute") %>%
  calculate(stat = "lm(mpg ~ hp)")
```

@@

One numerical (one mean)
```
mtcars %>%
  select(mpg) %>%
  generate(reps = 100, type = "bootstrap") %>%
  calculate(stat = "mean")
```
